Usability of Mobile Map Applications

### 2014-09-25 usability-study/usability-study.tex
add evaluation format

\begin{multicols}{2}
[
\section{Heuristic Evaluation}
Though usability metrics are extremely important in assessing a system, it is also important to heuristically evaluate systems in order to explore \textit{why} they performed the way they do.
My heuristic evaluations of the mobile map applications will be based on the guidelines documents that correspond to the applications. I will examine Google Maps first.
]
The icons of the Google Maps mobile application comply with the Google Design Guidelines\cite{Google}: simple, modern, geometric in execution, and with rounded corners. Be that as it may, Google Maps completely fails to use any standard iOS icons. Though it is not required to use these provided iOS icons, the iOS Human Interface Guidelines state that it is "a good idea to use the built-in icons as much as possible because users already know what they mean".\cite{Apple}
\includegraphics[width=.45\textwidth]{ios-bar-icons.png}
\includegraphics[width=.5\textwidth]{google-maps.png}

\end{multicols}
\clearpage
\begin{thebibliography}{100} % 100 is a random guess of the total number of 
%references
\bibitem{Nielsen} Nielsen, Jakob, \emph{Usability Engineering}, Boston: Academic, 1993.
\bibitem{Mossberg} Mossberg, Walt., ``The iPhone Takes to the Big Screen," \emph{The Wall Street Journal}, September 2012.
\bibitem{ComScore}``Analytics for a Digital World - ComScore, Inc." \emph{ComScore,Inc}, 2012.
\bibitem{Google} \emph{Material Design}, www.google.com/design/spec/material-design.
\bibitem{Apple} \emph{iOS Human Interface Guidelines}, https://developer.apple.com/library/ios/documentation/userexperience.
\end{thebibliography}
%%%%%%%%%%%%% end %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\begin{multicols}{2}
[
\section{Heuristic Evaluation}
Though usability metrics are extremely important in assessing a system, it is also important to heuristically evaluate systems in order to explore \textit{why} they performed the way they do.
My heuristic evaluations of the mobile map applications will be based on the guidelines documents that correspond to the applications.
\subsection{Google Maps}
]
The icons of the Google Maps mobile application comply with the Google Design Guidelines\cite{Google}: simple, modern, geometric in execution, and with rounded corners. Be that as it may, Google Maps completely fails to use any standard iOS icons:
\par
\noindent
\includegraphics[width=.45\textwidth]{ios-bar-icons.png}
\par
\noindent
Though it is not required to use these provided iOS icons, the iOS HIG (Human Interface Guidelines) state that it is ``a good idea to use the built-in icons as much as possible because users already know what they mean".\cite{Apple} Balancing consistency in platform with consistency of brand is a challenge, but there is a possibility that adhering more to the iOS HIG could improve usability of Google Maps. There was a higher percent of errors in clicking \underline{wrong icons} in the Google Maps application as there was in the Apple Maps application.

\includegraphics[width=.5\textwidth]{google-maps.png}

\end{multicols}
\clearpage
\begin{multicols}{2}
[
Though usability metrics are extremely important in assessing a system, it is also important to heuristically evaluate systems in order to explore \textit{why} they performed the way they do.
My heuristic evaluations of the mobile map applications will be based on the guidelines documents that correspond to the applications.
\subsection{Apple Maps}
]
\par
\noindent
\includegraphics[width=.49\textwidth]{apple-maps.png}
The icons of the Google Maps mobile application comply with the Google Design Guidelines\cite{Google}: simple, modern, geometric in execution, and with rounded corners. Be that as it may, Google Maps completely fails to use any standard iOS icons:
\par
\noindent
\includegraphics[width=.45\textwidth]{ios-bar-icons.png}
\par
\noindent
Though it is not required to use these provided iOS icons, the iOS HIG (Human Interface Guidelines) state that it is ``a good idea to use the built-in icons as much as possible because users already know what they mean".\cite{Apple} Balancing consistency in platform with consistency of brand is a challenge, but there is a possibility that adhering more to the iOS HIG could improve usability of Google Maps. There was a higher percent of errors in clicking \underline{wrong icons} in the Google Maps application as there was in the Apple Maps application.

\end{multicols}
\clearpage
\section{Conclusion}
Usability stuff goes here. blah blah blah
\clearpage
\begin{thebibliography}{100} % 100 is a random guess of the total number of 
%references
\bibitem{Nielsen} Nielsen, Jakob, \emph{Usability Engineering}, Boston: Academic, 1993.
\bibitem{Mossberg} Mossberg, Walt., ``The iPhone Takes to the Big Screen," \emph{The Wall Street Journal}, September 2012.
\bibitem{ComScore}``Analytics for a Digital World - ComScore, Inc." \emph{ComScore, Inc}, 2012.
\bibitem{Google} \emph{Material Design}, www.google.com/design/spec/material-design.
\bibitem{Apple} \emph{iOS Human Interface Guidelines}, https://developer.apple.com/
\end{thebibliography}
%%%%%%%%%%%%% end %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
